Debiased Calibration for Generalized Two-Phase Sampling

### 2024-04-16 final/reports/prelim_paper.tex
Updated prelim_paper.tex. Mostly finished with section 1.

\usepackage{amsmath, amssymb, amsthm, mathrsfs, fancyhdr}
\usepackage{syntonly, lastpage, hyperref, enumitem, graphicx}
\usepackage[style=authoryear]{biblatex}
\usepackage{booktabs}
\usepackage{float}

\addbibresource{references.bib}

\hypersetup{colorlinks = true, urlcolor = black}

\headheight     15pt
\topmargin      -1.5cm   % read Lamport p.163
\oddsidemargin  -0.04cm  % read Lamport p.163
\evensidemargin -0.04cm  % same as oddsidemargin but for left-hand pages
\textwidth      16.59cm
\textheight     23.94cm
\parskip         7.2pt   % sets spacing between paragraphs
\parindent         0pt   % sets leading space for paragraphs
\pagestyle{empty}        % Uncomment if don't want page numbers
\pagestyle{fancyplain}

@@

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

@@

@@

\begin{itemize}
\item Combining information from several sources is an important practical
  problem. 
\item In many cases, we do not have direct access to the other sources. We can
  only obtain summary statistics (and their standard errors) for the external
  data sources. We wish to incorporate the information from external  sources in
  our in-house data effectively using calibration weighting.  
\item We formulate the problem as a generalized two-phase sampling where the
  first phase sample can be obtained from multiple sources. The second-phase
  sample is our in-house data in which we want to construct the calibration
  weights. 
\item To achieve the goal, we first consider  the  classical two-phase sampling
  setup where the second-phase sample is a subset of the first-phase sample.
  After that, we extend the setup to more general cases such as non-nested
  two-phase sampling or multiple independent surveys with some common
  measurements. 
\item (To simplify the presentation, I wonder whether we can just use SRS in the
  first-phase sampling. ) 
\end{itemize}
\section{Topic 1: Classical Two-Phase Sampling}

\subsection{Background and Introduction}

Consider a finite population of size $N$ containing elements $(X_i, Y_i)$ where
an initial (Phase 1) sample of size $n$ is selected and $X_i$ is observed. Then
from the Phase 1 sample of elements, a (Phase 2) sample of size $r < n$ is
selected and $Y_i$ is observed. This is two-phase sampling (See 
\cite{fuller2009sampling}, \cite{kim2024statistics} for general references.) The
goal of two-phase sampling is to construct an estimator of $Y$ not
only using the observed information from the Phase 2 sample but also
incorporating the extra auxilary information of $X$ from the Phase 1 sample, and
the challenge is doing this efficiently.

An easy-to-implement unbiased estimator in the spirit of a Horvitz-Thompson
estimator (\cite{horvitz1952generalization}, \cite{narain1951sampling}) is the
$\pi^*$-estimator. Let $\pi_i^{(2)}$ be the response probability of element $i$
being observed in the Phase 2 sample. Then, allowing the elements in the Phase 1
sample to be represented by $A_1$ and the elements in the Phase 2 sample to be
denoted as $A_2$,

\begin{align*}
  \pi_i &= \sum_{A_2: i \in A_2} \Pr(A_2) \\ 
        &= \sum_{A_1: A_2 \subseteq A_1} \sum_{A_2: i \in A_2} \Pr(A_2 \mid
        A_1) \Pr(A_1) \\
        &= \sum_{A_1: i \in A_1} \sum_{A_2: i \in A_2} \Pr(A_2 \mid A_1) \Pr(A_1).
\end{align*}

If we define $\pi_{2i | 1}^{(2)} = \sum_{A_2: i \in A_2} \Pr(A_2 \mid A_1)$ and
$\pi_i^{(1)} = \sum_{A_1: i \in A_1} \Pr(A_1)$ then,

$$ \pi_i = \pi_{2i | 1}^{(2)} \pi_i^{(1)}.$$
\textcolor{red}{(note: there is an abuse of notation. You do not need to introduce superscript $(2)$ on $\pi_{2i \mid 1}$.) }
This means that we can define the $\pi^*$-estimator as the following design
unbiased estimator:

$$ \hat Y_{\pi^*} = \sum_{i \in A_2} \frac{y_i}{\pi_{2i | 1}^{(2)} \pi_i^{(1)}}.$$

While unbiased \cite{kim2024statistics}, the $\pi^*$-estimator unfortunately
does not account for the additional information contained in the auxiliary Phase
1 variable $X$. The two-phase regression estimator $\hat Y_{reg, tp}$ does incorporate 
\textcolor{blue}{$\hat{X}_1$ obtained from the phase one sample. That is, we can
leverage the external information $\hat{X}_1$ to improve the $\pi^*$-estimator
in the second-phase sample. } 
The two-phase regression estimator has the form,

$$ \hat Y_{reg, tp} 
= \sum_{i \in A_1} \frac{1}{\pi_i^{(1)}} x_i \hat \beta_2+ \sum_{i \in A_2}
\frac{1}{\pi_i^{(1)}\pi_{2i|1}^{(2)}} (y_i - x_i \hat \beta_2)$$
where $$\hat \beta_2 = \left(\sum_{i \in A_2} 
  \frac{x_i x_i'}{\pi_{2i|1}^{(2)}}\right)^{-1} 
  \sum_{i \in A_2} \frac{x_i y_i}{\pi_i^{(1)}\pi_{2i|1}^{(2)}}. 
  \footnote{Caleb, we do not have to use $\pi_{2i \mid 1}^{(2)}$ in computing $\hat{\beta}_2$. Please check my book. }
  $$

\textcolor{red}{I suggest that we use 
$$\hat \beta_2 = \left(\sum_{i \in A_2} 
  \frac{x_i x_i'}{\pi_{i}^{(1)} q_i }\right)^{-1} 
  \sum_{i \in A_2} \frac{x_i y_i}{\pi_i^{(1)} q_i }
$$ 
where $q_i=q(\bx_i)$ is a function of $\bx_i$. This will have some connection with model-optimal regression estimator (under superpopulation model).  
}

The regression
estimator is the minumum variance design consistent linear estimator which is
easily shown to be the case because $\hat Y_{reg, tp} = \sum_{i \in A_2} \hat
w_{2i} y_i / \pi_i^{(1)}$ where

$$\hat w_i = \argmin_{w} \sum_{i \in A_2} (w_i - \pi_{2i|1}^{-1})^2 \text{ such
that } \sum_{i \in A_2} w_i x_i / \pi_i^{(1)} = \sum_{i \in A_1} x_i /
\pi_i^{(1)}.$$

\textcolor{red}{Using $q_i$, we can construct 
$$\hat w_{2i} = \argmin_{w} \sum_{i \in A_2} (w_{2i} - \pi_{2i|1}^{-1})^2  q_i \text{ such
that } \sum_{i \in A_2} w_{2i}  x_i / \pi_i^{(1)} = \sum_{i \in A_1} x_i /
\pi_i^{(1)}$$
as a way to implement the two-phase regression estimator indirectly using calibration weighting. 
}

This means that $\hat Y_{reg, tp}$ is also a calibration estimator. The idea
that regression estimation is a form of calibration was extended by 
\cite{deville1992calibration} to consider loss functions other than just squared
loss. They generalized the loss function to minimize $\sum_i G(w_i, d_i)q_i$ for
weights $w_i$ and design-weights $d_i$ where $G(\cdot)$ is non-negative, strictly
convex function with respect to $w$, defined on an interval containing $d_i$,
with $g(w_i, d_i) = \partial G / \partial w$ continuous.
\footnote{The \cite{deville1992calibration} paper considers regression estimators
for a single phase setup, which we apply to our two-phase example. } This
generalization includes empirical likelihood estimation, and maximum entropy
estimation amoung others. The variance estimation is based on a linearization
that shows that minimizing the generalized loss function subject to the
calibration constraints is asymptotically equivalent to a regression estimator.

While this generalization is useful to an analyst who may want different
properties of their estimator from maximum entropy estimation rather than the
minimal squared loss, 
% TODO: I am not sure if this is correct -----
unless $\pi_{2i|1}^{-1} = x_i'a$ for some $a$, the
estimator is not design consistent. 
\footnote{ \textcolor{red}{I do not understand this part.} I changed the
notation so that it would not be the unused column space notation. This is from
Equation (11.17) of \cite{kim2024statistics}.} 
% --------------------------------------------

@@

$$ \hat Y_{reg, tp} 
= \underbrace{\sum_{i \in A_1} \frac{x_i \hat \beta_2}{\pi_i^{(1)}}}_{
  \text{ Minimizing the variance}} + \underbrace{\sum_{i \in A_2}
\frac{1}{\pi_i^{(1)}\pi_{2i|1}^{(2)}} (y_i - x_i \hat \beta_2)}_{
\text{Bias correction}}.$$

@@

Unfortunately, the method of \cite{kwon2024debiased} requires known calibration
levels (no uncertainty) for the finite population. It does not handle the
two-phase setup where we need to estimate the finite population total of $x$
from the Phase 1 sample. Hence, we extend this method to have a valid variance 
estimator when including estimated Phase 1 weights.

@@

@@

\begin{equation}\label{eq:primalloss}
H(w) = - \sum_{i \in A_2} G(w_i)
\end{equation}

@@

\begin{equation}\label{eq:calconst1}
\sum_{i \in A_2} \frac{x_i w_i}{\pi_i^{(1)}} = 
\sum_{i \in A_1} \frac{x_i}{\pi_i^{(1)}}
\end{equation}

@@

\begin{equation}\label{eq:calconst2}
\sum_{i \in A_2} \frac{g(\pi_{2i|1}^{-1})w_i}{\pi_i^{(1)}} = 
\sum_{i \in A_1} \frac{g(\pi_{2i|1}^{-1})}{\pi_i^{(1)}}.
\end{equation}

The first constraint is the existing calibration constraint and the second
ensures that design consistency is achieved. Here, $g(w) = \partial G / \partial
w$. The original method of \cite{kwon2024debiased} only considered having finite
population quantities on the right hand side of \ref{eq:calconst1}. Let $z_i =
(x_i, g(\pi_{2i|1}^{-1})$. To solve this minimization problem, we use the convex
conjugate function $F(w) = -G(g^{-1}) + g^{-1}(w)w$, and instead find

@@

\begin{itemize}
  \item[[A1]] $G(w)$ is strictly convex and twice differentiable in an interval
    $\mathcal{V} \in \R$,
  \item[[A2]] There exists $c_1, c_2 \in \mathcal{V}$ with $c_1, c_2 > 0$ such
    that $c_1 < \pi_{2i|1} < c_2$ for $i = 1, \dots, n$,
  \item[[A3]] If $\pi_{2ij|1}$ is joint inclusion probability of elements $i$
    and $j$ and $\Delta_{2ij|1} = \pi_{2ij|1} - \pi_{2i|1}\pi_{2j|1}$ then,
    $$\limsup_{n \to \infty} \max_{i,j \in A_1: i \neq j} |\Delta_{2ij|1}| <
    \infty,$$
  % TODO: Check if A4 should be stated for the finite population (as written) or
    % if this should be stated for the Phase 1 sample.
  \item[[A4]] Assume that $\Sigma_z = \lim_{N \to \infty} \sum_{i \in U} z_i
    z_i^T/N$ exists and is positive definite, the average fourth moment of $(y_i,
    x_i^T)$ is finite ($\limsup_{N \to \infty} \sum_{i \in U} ||(y_i, x_i^T)||^4
    / N < \infty$), and $\Gamma(\lambda) = \lim_{N \to \infty}  \sum_{i \in U}
    f'(\lambda^T z_i) z_i z_i^T / N$ exists in a neighborhood around $\lambda_0
    = (\bf 0, 1)$.
  \item[[A5]] FIXME: We need to make an assumption about how Phase 2 relates to
    Phase 1 which relates to the finite population.
\end{itemize}

\begin{theorem}{Design Consistency}
  Suppose that Conditions [A1] - [A5] hold. Then the solution $\hat w$ to 
  \ref{eq:primalloss} subject to \ref{eq:calconst1} and \ref{eq:calconst2} 
  exists and is unique with probability approaching 1. Furthermore, the
  estimator $\hat \theta_{DCE} = \sum_{i \in A_2} \frac{\hat w y_i}{\pi_i^{(1)}}$
  satisfies

  $$\hat \theta_{DCE} = \hat \theta_{DC} + o_p(FIXME)$$

@@

\begin{theorem}(Asymptotic Normality)
% FIXME: Add result.
\end{theorem}

% TODO: Provide asymptotic results showing the variance estimation of the
% estimated debiased calibration method
% DUE: Thursday April 11 (I have already showed the proof but I might finish the
% simulation study before writing this up.)

@@

% TODO: Conduct a simulation study highlighting the proposed method
% DUE: Friday April 12

>>>>

\usepackage{amsmath, amssymb, amsthm, mathrsfs, fancyhdr}
\usepackage{syntonly, lastpage, hyperref, enumitem, graphicx}
%\usepackage[style=authoryear]{biblatex}
\usepackage{booktabs}
\usepackage{float}

\usepackage{amsmath, amsthm, mathtools,commath}
\usepackage{graphics, color}
\usepackage{latexsym}
\usepackage{amssymb, amsfonts, bm}
\usepackage{mathrsfs}

\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{makeidx}
\usepackage{fullpage}
\usepackage{booktabs, arydshln}
\usepackage{comment} 
%\makeindex

\hbadness=10000 \tolerance=10000 \hyphenation{en-vi-ron-ment
in-ven-tory e-num-er-ate char-ac-ter-is-tic}

\usepackage[round]{natbib}
%\bibliographystyle{apalike2}
% \bibliographystyle{jmr}

\newcommand{\biblist}{\begin{list}{}
{\listparindent 0.0cm \leftmargin 0.50cm \itemindent -0.50 cm
\labelwidth 0 cm \labelsep 0.50 cm
\usecounter{list}}\clubpenalty4000\widowpenalty4000}
\newcommand{\ebiblist}{\end{list}}

\newcounter{list}

%\usepackage{setspace}

%\usepackage{hangpar}
\newcommand{\lbl}[1]{\label{#1}{\ensuremath{^{\fbox{\tiny\upshape#1}}}}}
% remove % from next line for final copy
\renewcommand{\lbl}[1]{\label{#1}}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\newtheorem{remark}{Remark}
\newtheorem{result}{Result}

\newtheorem{lemma}{Lemma}

@@

@@

\baselineskip .3in

@@

Combining information from several sources is an important practical problem. (CITEME)
We want to incorporate information from external data sources to reduce the bias
in our estimates or improve the estimator's efficiency. For many problems, the
additional information consist of summary statistics with standard errors. The
goal of this project is to incorporate external information with existing data 
to create more efficient estimators using calibration weighting.

To model this scenaro, we formulate the problem as a generalized two-phase
sample where the first phase sample consists of data from multiple sources. The
second phase sample contains our existing data. To motivate this setup, we
consider the following approach: first, we consider the classical two-phase
sampling setup where the second phase sample is a subset of the first phase
sample; then, we extend this setup to consider non-nested two-phase samples;
and finally, we consider the more general approach of having multiple sources as
the first phase sample.

%\begin{itemize}
%\item To achieve the goal, we first consider  the  classical two-phase sampling
%setup where the second-phase sample is a subset of the first-phase sample.
%  After that, we extend the setup to more general cases such as non-nested
%  two-phase sampling or multiple independent surveys with some common
%  measurements. 
%\item The proposed method can be called two-step calibration. In the
%first-step, the best linear unbiased estimators of the auxiliary variable
%totals are computed. In the second-step, the final calibration weights are
%constructed to match (benchmark) with the best estimators computed from Step 1. 
%\end{itemize}

\section{Topic 1: Classical Two-Phase Sampling}

\subsection{Background}

Consider a finite population of size $N$ containing elements $(X_i, Y_i)$ where
an initial (Phase 1) sample of size $n$ is selected and $X_i$ is observed. Then
from the Phase 1 sample of elements, a (Phase 2) sample of size $r < n$ is
selected and $Y_i$ is observed. This is two-phase sampling (See 
\cite{fuller2009sampling}, \cite{kim2024statistics} for general references.) The
goal of two-phase sampling is to construct an estimator of $Y$ not
only using the observed information from the Phase 2 sample but also
incorporating the extra auxiliary information of $X$ from the Phase 1 sample, and
the challenge is doing this efficiently.

An easy-to-implement unbiased estimator in the spirit of a Horvitz-Thompson (HT)
estimator (\cite{horvitz1952generalization}, \cite{narain1951sampling}) is the
$\pi^*$-estimator. Let $\pi_i^{(2)}$ be the response probability of element $i$
being observed in the Phase 2 sample. Then, allowing the elements in the Phase 1
sample to be represented by $A_1$ and the elements in the Phase 2 sample to be
denoted as $A_2$,
%\begin{align*}
%  \pi_i &= \sum_{A_2: i \in A_2} \Pr(A_2) \\ 
%        &= \sum_{A_1: A_2 \subseteq A_1} \sum_{A_2: i \in A_2} \Pr(A_2 \mid
%        A_1) \Pr(A_1) \\
%        &= \sum_{A_1: i \in A_1} \sum_{A_2: i \in A_2} \Pr(A_2 \mid A_1) \Pr(A_1).
%\end{align*}
%\textcolor{red}{(I am not sure whether this part is necessary.) }
if we define $\pi_{2i | 1} = \sum_{A_2: i \in A_2} \Pr(A_2 \mid A_1)$ and
$\pi_{1i} = \sum_{A_1: i \in A_1} \Pr(A_1)$ then,

$$ \pi_i(A_1) = \pi_{2i | 1} \pi_{1i}.$$

%\textcolor{red}{Also, the above equality is not true under two-phase sampling!)}
\textcolor{red}{I agree that having the superscript $(1)$ and $(2)$ is
  unnecessary. I have removed them. I have also modified the previous equation.
  I agree that the invariance condition does not hold for two-phase sampling,
  but if we consider $\pi_i$ as a function of $A_1$ then I believe this holds.
  Is this correct? Should we not have $\pi_{i} = \pi_{1i} \pi_{2i|1}(A_1)$
  because this is how conditional distributions work? (Also, I thought that this
  is equivalent to the reverse sampling idea of Fey (1992), Shao and Steel
(1999), and Kim et al. (2006).) I would love to discuss this with you.}

This means that we can define the $\pi^*$-estimator as the following design
unbiased estimator:

$$ \hat Y_{\pi^*} = \sum_{i \in A_2} \frac{y_i}{\pi_{2i | 1} \pi_{1i}}.$$

While unbiased (see \cite{kim2024statistics}), the $\pi^*$-estimator
does not account for the additional information contained in the auxiliary Phase
1 variable $X$. The two-phase regression estimator $\hat Y_{reg, tp}$ does incorporate 
information for $X$ by using the estimate $\hat X_1$ from the Phase 1 sample.
This is how we can leverage the external information $\hat X_1$ to improve the
initial $\pi^*$-estimator in the second phase sample.
The two-phase regression estimator has the form,

$$ \hat Y_{reg, tp} 
= \sum_{i \in A_1} \frac{1}{\pi_{1i}} x_i \hat \beta_2+ \sum_{i \in A_2}
\frac{1}{\pi_{1i}\pi_{2i|1}} (y_i - x_i \hat \beta_2)$$

where for $q_i = q(x_i)$ and is a function of $x_i$,
$$
\hat \beta_2 = \left(\sum_{i \in A_2} 
  \frac{x_i x_i'}{\pi_{1i} q_i}\right)^{-1} 
\sum_{i \in A_2} \frac{x_i y_i}{\pi_{1i} q_i}. 
\footnote{
  \textcolor{blue}{Caleb, we do not have to use $\pi_{2i \mid 1}^{(2)}$ in computing
  $\hat{\beta}_2$. Please check my book.}
  \textcolor{red}{Thanks for the check. I
checked it and I must have gotten $\pi_{1i}$ and $\pi_{2i}$ confused.}}
\footnote{\textcolor{red}{I was initially thinking of using $\hat \beta_2$ without $q_i$ to be
  more consistent with how I defined the two-phase regression estimator;
  however, I see your point about using $q_i$ to connect this estimator with the
superpopulation model.}}
  $$

The regression estimator is the minimum variance design consistent linear
estimator which is easily shown to be the case because $\hat Y_{reg, tp} =
\sum_{i \in A_2} \hat w_{2i} y_i / \pi_{1i}$ where

$$\hat w_{2i} = \argmin_{w} \sum_{i \in A_2} (w_{2i} - \pi_{2i|1}^{-1})^2 q_i \text{ such
that } \sum_{i \in A_2} w_{2i} x_i / \pi_{1i} = \sum_{i \in A_1} x_i / \pi_{1i}.$$

This means that $\hat Y_{reg, tp}$ is also a calibration estimator. The idea
that regression estimation is a form of calibration was extended by 
\cite{deville1992calibration} to consider loss functions other than just squared
loss. They generalized the loss function to minimize $\sum_i G(w_i, d_i)q_i$ for
weights $w_i$ and design-weights $d_i$ where $G(\cdot)$ is non-negative, strictly
convex function with respect to $w$, defined on an interval containing $d_i$,
with $g(w_i, d_i) = \partial G / \partial w$ continuous.
\footnote{The \cite{deville1992calibration} paper considers regression estimators
for a single phase setup, which we apply to our two-phase example. } This
generalization includes empirical likelihood estimation, and maximum entropy
estimation among others. The variance estimation is based on a linearization
that shows that minimizing the generalized loss function subject to the
calibration constraints is asymptotically equivalent to a regression estimator.

While this generalization is useful to an analyst who may want different
properties of their estimator from maximum entropy estimation rather than the
minimal squared loss, 
% TODO: I am not sure if this is correct -----
unless $\pi_{2i|1}^{-1} = x_i'a$ for some $a$, the
estimator is not design consistent. 
\footnote{ \textcolor{blue}{I do not understand this part.} 
  \textcolor{red}{I changed the
notation so that it would not be the unused column space notation. This is from
Equation (11.17) of \cite{kim2024statistics}.}} 
\footnote{\textcolor{red}{I think that I am confused about the purpose of having
the assumption from Equation (11.17) in your sampling book. Could we discuss
this?}}
% --------------------------------------------

@@

$$ \hat Y_{reg, tp} 
= \underbrace{\sum_{i \in A_1} \frac{x_i \hat \beta_2}{\pi_{1i}}}_{
  \text{ Minimizing the variance}} + \underbrace{\sum_{i \in A_2}
\frac{1}{\pi_{1i}\pi_{2i|1}} (y_i - x_i \hat \beta_2)}_{
\text{Bias correction}}.$$

@@

The method of \cite{kwon2024debiased} requires known calibration
levels (no uncertainty) for the finite population. It does not handle the
two-phase setup where we need to estimate the finite population total of $x$
from the Phase 1 sample. Hence, we extend this method to have a valid variance 
estimator when including estimated Phase 1 weights.

@@

%The proposed method will be something like this: 
%\textcolor{red}{Minimize 
%  $$ \sum_{i \in A_2} \frac{1}{\pi_i^{(1)}}  G( w_{2i} ) q_i $$ 
%  subject to 
%  $$ \sum_{i \in A_2} w_{2i}  x_i / \pi_i^{(1)} = \sum_{i \in A_1} x_i / \pi_i^{(1)}$$ 
%  and 
%  $$ \sum_{i \in A_2}  \frac{1}{\pi_i^{(1)}} w_{2i} g( \pi_{2i \mid 1}^{-1} ) q_i
%  = \sum_{i \in A_1}  \frac{1}{\pi_i^{(1)}}  g(\pi_{2i \mid 1}^{-1} ) q_i $$ 
%  where $g(\omega) = \partial G( \omega)/ \partial \omega$. }

% You need to show that the resulting calibration estimator $\hat{Y}_{\rm cal}=
% \sum_{i \in A_2} w_{1i} \hat{w}_{2i} y_i$ is asymptotically equivalent to the
% two-phase regression estimator in (\ref{reg}), where $w_{1i} = 1/ \pi_i^{(1)}$.

% Also, there should be a discussion about variance estimation. Once the
% linearization form is obtained, the formula for linearized variance estimation
% should be obtained easily.

@@

\begin{equation}\label{eq:primalloss}
  H(w) = - \sum_{i \in A_2} \frac{1}{\pi_{1i}} G(w_{2i}) q_i
\end{equation}

@@

\begin{equation}\label{eq:calconst1}
  \sum_{i \in A_2} \frac{x_i w_{2i}}{\pi_{1i}} = 
\sum_{i \in A_1} \frac{x_i}{\pi_{1i}}
\end{equation}

@@

\begin{equation}\label{eq:calconst2}
  \sum_{i \in A_2} \frac{g(\pi_{2i|1}^{-1})w_{2i}q_i}{\pi_{1i}} = 
  \sum_{i \in A_1} \frac{g(\pi_{2i|1}^{-1})q_i}{\pi_{1i}}.
\end{equation}

The first constraint is the existing calibration constraint and the second
ensures that design consistency is achieved. Here, 
$g(w) = \partial G / \partial w$. 
% TODO: Elaborate on this more.
The original method of \cite{kwon2024debiased} only considered having finite
population quantities on the right hand side of \ref{eq:calconst1}.
Let $z_i =
(x_i, g(\pi_{2i|1}^{-1})$. To solve this minimization problem, we use the convex
conjugate function $F(w) = -G(g^{-1}) + g^{-1}(w)w$, and instead find

@@

\begin{itemize}
  \item[(A1)] $G(w)$ is strictly convex and twice differentiable in an interval
    $\mathcal{V} \in \R$,
  \item[(A2)] There exists $c_1, c_2 \in \mathcal{V}$ with $c_1, c_2 > 0$ such
    that $c_1 < \pi_{2i|1} < c_2$ for $i = 1, \dots, n_2$, and 
    that $c_1 < \pi_{1i} < c_2$ for $i = 1, \dots, n_1$,
  \item[(A3)] If $\pi_{2ij|1}$ is joint inclusion probability of elements $i$
    and $j$ in $A_2$, the Phase 2 sample and 
    $\Delta_{2ij|1} = \pi_{2ij|1} - \pi_{2i|1}\pi_{2j|1}$ then,
    $$\limsup_{n \to \infty} \max_{i,j \in U: i \neq j} |\Delta_{2ij|1}| <
    \infty,$$
    and if $\pi_{1ij}$ is the joint inclusion probability of elements $i$ and
    $j$ in $A_1$, the Phase 1 sample and 
    $\Delta_{1ij} = \pi_{1ij} - \pi_{1i}\pi_{1j}$ then,
    $$\limsup_{n \to \infty} \max_{i,j \in U: i \neq j} |\Delta_{1ij}| <
    \infty,$$
  \item[(A4)] Assume that $\Sigma_z = \lim_{N \to \infty} \sum_{i \in U} z_i
    z_i^T/N$ exists and is positive definite, the average fourth moment of $(y_i,
    x_i^T)$ is finite ($\limsup_{N \to \infty} \sum_{i \in U} ||(y_i, x_i^T)||^4
    / N < \infty$), and $\Gamma(\lambda) = \lim_{N \to \infty}  \sum_{i \in U}
    f'(\lambda^T z_i) z_i z_i^T / N$ exists in a neighborhood around $\lambda_0
    = (\bf 0, 1)$.
\end{itemize}

\begin{theorem}[Design Consistency]
  Suppose that Conditions (A1) - (A4) hold. Then the solution $\hat w$ to 
  Equation~\ref{eq:primalloss} subject to Equation~\ref{eq:calconst1} and 
  Equation~\ref{eq:calconst2} 
  exists and is unique with probability approaching 1. Furthermore, the
  estimator $\hat \theta_{DCE} = \sum_{i \in A_2} \frac{\hat w_i y_i}{\pi_{1i}}$
  satisfies

  $$\hat \theta_{DCE} = \hat \theta_{DC} + o_p(n_2^{-1})$$

@@

\begin{proof}
  This proof follows the proof of \cite{kwon2024debiased} in a straightforward
  manner. There are two main modifications that need to be made. The first is
  that the proof needs to be written for two-phase sampling with $n_1$ and $n_2$
  instead of a single $n$. The second is that we need to ensure that the result
  still holds with an estimated population constraint that is $O_p(n_1^{-1/2})$
  consistent.

  With the Conditions (A1) - (A4) written with respect the the two-phase sample,
  the first challenge is done. The second step largely holds from the existing
  proof of \cite{kwon2024debiased} with modifications such as

  $$\hat Q(\lambda) = n_2^{-1} \sum_{i \in A_2} F(\lambda^T z_i^*) - n_1^{-1}
  \lambda^T \sum_{i \in A_1} z_i^*$$

  ensuring that our extension holds.

  \textcolor{red}{Dr. Kim, I know that I need to write up this proof in more
  detail, but I am unsure about the level of granularity that is required now. I
  can basically rewrite everything from the Appendix of \cite{kwon2024debiased}
  with the two-phase modification to show this result, but I don't know if I
  should yet.}
\end{proof}

We need the following additional assumptions to prove asymptotic normality.

% FIXME: Add assumptions
\textcolor{red}{I need to think about the assumptions that we need in two-phase
sampling.}
\begin{itemize}
  \item[(B1)] 
  \item[(B2)] The HT estimator is asymptotically normal under the sampling
    design in the sense that

\end{itemize}

\begin{theorem}[Asymptotic Normality]
% FIXME: Add result.
\textcolor{red}{I need to write out more but we should have something like this:
  $$V(\hat \theta_{DCE} = \Var(\hat \theta_{DC}) + \hat \gamma_{[1:3]}^T V(\bf
x)) \hat \gamma_{[1:3]} + \Cov(\hat \theta_{DC}, \bf x \hat \gamma_{[1:3}]).$$}
\end{theorem}

\textcolor{red}{Dr. Kim, I am not convinced that $\Cov(\hat \theta_{DC}, \bf x
\hat \gamma_{[1:3]}) = 0$. The reason that this covariance holds in
\cite{fuller2009sampling} Section 3.3.3 is that the estimating equation requires
$\sum_i x_i \hat e_i = 0$, which means that $\Cov(\hat e, x_i) = 0$. However, we
do not have this requirement. Instead, I see this more like a nested model where
we have a group level error that aggregates the individual level errors. The
problem with the current simulation that I cannot tell if this covariance should
be zero because the variance term $\hat \gamma_{[1:3]}'V(\bf x) \hat \gamma_{[1:3]}$
dominates the variance estimation. I will change the simulation parameters to
try to see if I can get a better test of this.}

@@

We run a simulation testing the proposed method. In this approach we have the
following simulation setup:

$$
\begin{aligned}
X_{1i} &\stackrel{ind}{\sim} N(2, 1) \\
X_{2i} &\stackrel{ind}{\sim} Unif(0, 4) \\
X_{3i} &\stackrel{ind}{\sim} N(0, 1) \\
X_{4i} &\stackrel{ind}{\sim} Unif(0.1, 0.9) \\
\varepsilon_i &\stackrel{ind}{\sim} N(0, 1) \\
Y_{i} &= 3 X_{1i} + 2 X_{2i} + \varepsilon_i \\
\pi_{1i} &= \Phi_3(-x_{3i} - 2) \\
\pi_{2i|1} &= x_{4i}.
\end{aligned}
$$

where $\Phi_3$ is the CDF of a t-distribution with 3 degrees of freedom.
This is a two-phase extension of the setup in \cite{kwon2024debiased}. We
consider a finite population of size $N = 10,000$ with both the Phase 1 and
Phase 2 sampling occuring under Poisson (Bernoulli) sampling. This yields a
Phase 1 sample
size of $E[n_1] \approx 1100$ and a Phase 2 sample size of
$E[n_2] \approx 550$. In the Phase 1 sample, we observe 
$(X_1, X_2)$ while in the Phase 2 sample we observe $(X_1, X_2, Y)$. This
simulation does not deal with model misspecification, and we compare the
proposed method for the parameter $\bar Y_N$ with four approaches:

\begin{itemize}
  \item[1.] $\pi^*$-estimator: $\hat Y_{\pi^*} = N^{-1} \sum_{i \in A_2}
    \frac{y_i}{\pi_{1i} \pi_{2i|1}},$
  \item[2.] Two Phase Regression estimator (TP-Reg): 
    $\hat Y_{reg} = \sum_{i \in A_1} \frac{\bf x_i' \hat \beta}{\pi_{1i}} + 
    \sum_{i \in A_2} \frac{1}{\pi_{1i}\pi_{2i|1}}(y_i - \bf x_i' \hat \beta)$ 
    where $\hat \beta = 
    \left(\sum_{i \in A_2} \bf x_i \bf x_i'\right)^{-1} \sum_{i \in A_2} \bf x_i y_i$
    and $\bf x_i = (x_{1i}, x_{2i})^T$,
    \textcolor{red}{Dr. Kim, should I modify the simulation so that the
    regression estimator also includes $g(\pi_{2i|1}^{-1})$ as a covariate?}
  \item[3.] Debiased Calibration with Population Constraints (DC-Pop): This is
    the method from \cite{kwon2024debiased} with the true population level
    constraints, and 
  \item[4.] Debiased Calibration with Estimated Population Constraints (DC-Est):
    This is the proposed method with the Phase 1 sample being used to estimate
    the population level constraints.
\end{itemize}

In addition to estimating the mean parameter $\bar Y_N$, we also construct
variance estimates $\hat V(\hat Y)$ for each estimate $\hat Y$. For each
approach we have the following variance estimate\footnote{These variance
estimates use the fact that we have Poisson sampling for both phases in the
simulation.}:

\begin{figure}[ht!]
  \centering
  \begin{tabular}{lcc}
    \toprule
    Estimator & Variance & Notes \\
    \midrule
    $\pi^*$ & $N^{-2} \sum_{i \in A_2} \left(\pi_{2i|1}^{-2} - \pi_{2i|1}^{-1}\right)
    y_i^2 $ & \\
    TP-Reg  & 
      {\scriptsize $N^{-2}\left(\sum\limits_{i \in A_1} \left(\pi_{1i}^{-2} -
          \pi_{1i}^{-1}\right) 
      \eta_i^2 
      + \sum\limits_{i \in A_2} \frac{1}{\pi_{1i} \pi_{2i|1}}(\pi_{2i|1}^{-1}
  - 1) (y_i - \bf x_i' \hat \beta)^2 \right)$}
    & 
      {\scriptsize$\eta_i = \bf x_i \hat \beta + \frac{\delta_{2i}}{\pi_{2i|1}}(y_i - 
      \bf x_i \hat \beta)$} \\
      %$\hat \beta = \left(\sum_{i \in A_2} \bf x_i \bf x_i'\right)^{-1} \sum_{i \in A_2} \bf x_i y_i$ \\
      DC-Pop  & $(Y - \bf z^T \hat \gamma)^T \Pi (Y - \bf z^T \hat \gamma)$ & 
      {\scriptsize$\Pi
      = \text{diag}(1 - (\pi_{1}\pi_{2|1})^{-1}) \cdot \frac{\hat w^2}{N^2}$} \\
      DC-Est  & $(Y - \bf z^T \hat \gamma)^T \Pi (Y - \bf z^T \hat \gamma) +
      \hat \gamma_{[1:3]}^T V(\bf x) \hat \gamma_{[1:3]}/N^2$ & \\
    \bottomrule
  \end{tabular}
  \caption{This table gives the formulas for each variance estimator used in
  this simulation.}
  \label{tab:varforms}
\end{figure}

We run this simulation $1000$ times for each of these methods and compute the
Bias ($E[\hat Y] - \bar Y_N$), the RMSE ($\sqrt{\Var(\hat Y - \bar Y_N)}$), a 95\%
empirical confidence interval ($\sum_{b = 1}^{1000} |\hat Y^{(b)} - \bar Y_N| \leq 
\Phi(0.975)\sqrt{\hat V(\hat Y^{(b)})^{(b)}}$), and a T-test that assesses the
unbiasedness of each estimator. The results are in Figure~\ref{fig:tpdc-mean}.

\begin{figure}[ht!]
  \centering
\input{tables/tpdcsim_mean.tex}
% This table was generated from /src/explore/20240411-tpdcsim.qmd
\caption{This table shows the results of the simulation study. It displays the
Bias, RMSE, empirical 95\% confidence interval, and a t-statistic assessing the
unbiasedness of each estimator for the estimators: $\pi^*$, TP-Reg, DC-Pop, and
DC-Est.}
\label{fig:tpdc-mean}
\end{figure}
